Analysis of split plot design using MCMCglmm

### 2017-08-25 README.Rmd
Clarify a few points in README

The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect pests and sheath blight disease in rice paddies.

@@

**Objective:** Study the effects of different water and nitrogen managements on sheath blight of rice

>>>>

The goal of _rice.awd.shb_ is to examine the effects of using alternate wetting and drying irrigation techniques on insect populations and sheath blight disease in rice paddies.

@@

**Objective 1:** Study the effects of different water and nitrogen managements on sheath blight of rice
